DeloreanJS: Un Debugger en el Tiempo para JavaScript

### 2019-04-09 paper/main.tex
final

\author{\IEEEauthorblockN{Paul Leger}
\IEEEauthorblockA{\textit{Escuela de Ingenier\'ia} \\
\textit{Universidad Cat\'olica del Norte}\\
Coquimbo, Chile \\
pleger@ucn.cl}
\and
\IEEEauthorblockN{AAAA BBBB}
\IEEEauthorblockA{\textit{Escuela de Ingenier\'ia} \\
\textit{Universidad Cat\'olica del Norte}\\
Coquimbo, Chile \\
aaaa.bbbb@alumnos.ucn.cl}
\and
\IEEEauthorblockN{XXXX YYYY}
\IEEEauthorblockA{\textit{Escuela de Ingenier\'ia} \\
\textit{Universidad Cat\'olica del Norte}\\
Coquimbo, Chile \\
xxxx.yyyy@alumnos.ucn.cl}
}

>>>>

\author{\IEEEauthorblockN{Paul Leger}
\IEEEauthorblockA{\textit{Escuela de Ingenier\'ia} \\
\textit{Universidad Cat\'olica del Norte}\\
Coquimbo, Chile \\
pleger@ucn.cl}
\and
\IEEEauthorblockN{Felipe Ruiz}
\IEEEauthorblockA{\textit{Escuela de Ingenier\'ia} \\
\textit{Universidad Cat\'olica del Norte}\\
Coquimbo, Chile \\
felipe.ruiz@alumnos.ucn.cl}
\and
\IEEEauthorblockN{Guillermo Victorero}
\IEEEauthorblockA{\textit{Escuela de Ingenier\'ia} \\
\textit{Universidad Cat\'olica del Norte}\\
Coquimbo, Chile \\
guillermo.victorero@alumnos.ucn.cl}
}
